Accelerated convergence of convective simulations using boundary value problems

### 2018-02-06 tex/bvp_paper.tex
moving a fig to the bottom of page for cleanliness
paper is better

\begin{abstract}
We present a method for coupling Boundary value problems (BVPs) with Initial value problems (IVPs)
in order to achieve thermally converged convective solutions on dynamical timescales, rather than the
long thermal timescale.  We demonstrate the similarity between the solution reached by BVP and the
solution reached by a long thermal rundown of the IVP, and demonstrate that this method works at a
large range of supercriticalities.  We use this method to achieve converged solutions at high Ra,
and discuss its extension to more complex scenarios, such as stratified, compressible convection.
\end{abstract}
\maketitle

\section{Introduction}
\label{sec:intro}
Natural convection occurs in the presence of disparate timescales. Granules on the
solar surface overturn on the order of 10 minutes, whereas deep motions in the Sun are likely at
low Mach number and constrained by the solar rotation rate of $\sim$1 month.  
Both of these dynamical timescales are vastly shorter than the Sun's average timescale of energy transport,
which is the Kelvin-Helmholtz timescale of nearly $3 \times 10^7$ \emph{years} \cite{stix2003}. 
As simulations aim to model natural convection
by increasing into the high-Rayleigh Number (Ra) regime, where diffusive timescales are much
longer than dynamical timescales \cite{anders&brown2017}, achieving converged simulations will 
require runs which span a greater number of convective timescales in order to thermally converge.
Furthermore, with increasing Ra and decreasing diffusivities, motions become more turbulent
and require finer grid meshes and shorter timesteps to resolve turbulent motions, increasing the simulation
time required for each overturn timescale.  
These two effects conspire to make achieving thermally converged, high-Ra, astrophysically interesting
simulations an intractable problem using modern numerical tools.

@@

\section{Experiment}
\label{sec:experiment}
We adopt the Oberbeck-Boussinesq approximation.  Under this choice, the
fluid has constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
of thermal expansion ($\alpha$). The variables of the fluid that are evolved are the velocity,
$\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$, the temperature $T = T_0 + T_1$, and the pressure, $P$.
The density of the fluid is a constant $\rho_0$, except on the
term where the constant gravitational acceleration, $\bm{g} = - g\hat{z}$ acts in the vertical momentum equation, 
in which case it is $\rho = \rho_0(1  - \alpha T_1)$.  
Under these choices, the equations of motion are \cite{spiegel&veronis1960}
\begin{gather}
\DivU = 0, 
	\label{eqn:dim_incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
-\frac{1}{\rho_0}\grad P - g( 1 - \alpha T_1)\hat{z} + \nu\grad^2\bm{u}, 
	\label{eqn:dim_bouss_momentum}
\\
\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \kappa\grad^2 T_1,
	\label{eqn:dim_bouss_energy}
\end{gather}
We non-dimensionalize these equations such that length scales are in units of the layer height ($L_z$),
temperature is in units of the initial temperature jump across the layer ($\Delta T_0 = L_z \grad T_0$), 
and time is in units of the freefall timescale ($L_z / v_{\text{ff}}$), where the freefall velocity is
$v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$.
We further re-arrange the momentum equation by introducing a reduced kinematic pressure,
$\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$, where $\bm{g} = -\grad \phi$ is the gravitational potential.
Despite containing a nonlinear $\bm{u}$ component, the nature of $P$ in \RB convection, as a
Lagrange multiplier,
allows us to treat $\varpi$ as a linear unknown, without a need to resolve its different components.
We time evolve the equations in the form,
\begin{gather}
\DivU = 0, 
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} = \bm{u}\times\bm{\omega}
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} = - \bm{u}\cdot\grad T_1,
	\label{eqn:bouss_energy}
\end{gather}
where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity. We find Eq. (\ref{eqn:bouss_momentum}) to
be slightly faster numerically than the standard form in Eq. (\ref{eqn:dim_bouss_momentum}).
The dimensionless control parameters are set by the Rayleigh and Prandtl numbers,
\begin{equation}
\mathcal{R} \equiv \sqrt{\frac{\text{Pr}}{\text{Ra}}}, \qquad \mathcal{P} \equiv \frac{1}{\sqrt{\text{Pr}\,\text{Ra}}}, \qquad
\text{Ra} = \frac{g \alpha L_z^4 \grad T_0}{\nu\chi} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\chi}, \qquad \text{Pr} = \frac{\nu}{\chi}.
\end{equation}
The dimensionless vertical extent of the domain is $z = [-1/2, 1/2]$, and at the boundaries
we impose no-slip, impenetrable boundary conditions such that $w = u = v = 0$ at $z = \pm 1/2$.
At the lower boundary, we employ a fixed flux condition such that $\partial T_1 / \partial z = 0$
at $z = -1/2$, and we impose a fixed temperature condition $T_1 = 0$ at $z = 1/2$. Both
horizontal directions are periodic, extending over a range $x, y = [0, \Gamma]$, where
the aspect ratio is $\Gamma = 2$. In our 2D cases, we only examine the $x$ and $z$ dimensions
and we set $v = \partial_y = 0$.

The chosen thermal boundary conditions at the upper and lower plates
determine key quantities of the evolved state.
Studies of incompressible, Boussinesq, \RB convection often
employ fixed temperature (Dirichlet) or fixed heat flux
(Neumann) boundary conditions at both plates.  
Dirichlet conditions represent plates of infinite conductivity,
whereas Neumann conditions model plates of finite conductivity.  
In both cases, choosing symmetric boundary conditions maintains overall system symmetry, 
and despite evolving towards different thermal structures, both types of conditions
transport heat in the same manner \cite{johnston&doering2009}.
Studies of convection which aim to model
astrophysical systems such as stars often employ a mixture of these
two types of boundary conditions \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.  
The flux at the lower boundary is fixed, modeling
the constant energy generation of the stellar core, 
while the outer boundary condition is held at a fixed temperature,
modeling the surface of a star which must output the energy generated internally.
This setup is a useful model for understanding natural
systems, but simulations which employ these boundary conditions suffer from a long 
thermal relaxation as the atmosphere loses energy and approaches the adiabat chosen by the
Dirichlet condition.  We choose these conditions in part to better understand them, and in
part because these conditions minimize the number of assumptions that must be made in
setting up the boundary value problem.  For this choice of boundary conditions, the
critical Ra is Ra$_{\text{crit}} = 1295.78$, and we will often speak in terms of the
supercriticality, $S = \text{Ra}/\text{Ra}_{\text{crit}}$.

@@

\subsection{Numerics}
We utilize the 
Dedalus\footnote{\url{http://dedalus-project.org/}} 
pseudospectral framework \cite{burns&all2016} to time-evolve  
(\ref{eqn:incompressible})-(\ref{eqn:bouss_energy}) 
using an implicit-explicit (IMEX), third-order, four-step 
Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
The temperature field is decomposed as $T = T_0(z) + T_1(x, y, z, t)$
and the velocity is $\bm{u} = w\bm{\hat{z}} + u\bm{\hat{x}} + v\bm{\hat{y}}$.
In our 2D runs, $v = 0$.
Variables are time-evolved on a dealiased Chebyshev (vertical)
and Fourier (horizontal, periodic) domain in which the
physical grid dimensions are 3/2 the size of the coefficient grid.

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
\caption{Comparisons of the evolved thermodynamic states of a BVP solution and a long IVP rundown at
$S = 10^{4 + 2/3}$ are shown.  (a) Evolved temperature profiles, as a function of height.
(b) The percentage difference between the temperature profiles (as shown in (a)), as a function of height.
(c) Frequency distributions of point-by-point measurements of $T$ throughout the two domains over the
averaging windows are shown.
The BVP shows excellent agreement with the thermal rundown (AUTHOR NOTE: I need to perform quantitative PDF
comparisons, still).
\label{fig:temp_comparison} }
\end{figure}

The temperature profiles of a 2D run at $S = 10^{4 + 2/3}$ 
for both the BVP solve and the long rundown are shown in
Fig. \ref{fig:temp_comparison}a.  While they are not perfectly aligned they are within less than
0.25\% of each other throughout the depth of the atmosphere, as shown in Fig. \ref{fig:temp_comparison}b.
While the mean temperature profile is interesting, the point-by-point fluctuations in the
temperature are what lead to convective transport, and thus examining the spread of temperature
and the allowed values that it can take are important to characterizing the system.  As seen
in Fig. \ref{fig:temp_comparison}c, aside from the noticeable difference in the mode of the
temperatures, the two runs exhibit largely the same spread of temperatures.
(AUTHOR NOTE: I'll run a Kolmogorov-Smirnov test to compare the PDFs, but I need to collaborate on this
to make sure that what I'm planning on doing makes sense -- we should talk about this.)

In addition to examining the thermodynamics of the solutions, we are especially interested in
determining if the post-BVP solution appropriately captures key features of the nonlinear dynamics.
We show point-by-point frequency distributions of the horizontal velocity, vertical velocity,
and nonlinear transport in Fig. \ref{fig:pdf_comparison}.  All of these measures have a sharp
peak at zero due to the no-slip, impenetrable boundary conditions and the denser grid sampling
near the boundaries of our Chebyshev grid.  Regardless, we see that the velocities of the 
two solutions are largely consistent.  The nonlinear transport in Fig. \ref{fig:pdf_comparison}
shows that the rundown solution experiences more extreme events which carry a large amount of
flux than the BVP solution, but the distributions are largely consistent.
(AUTHOR NOTE: see previous paragraph comment).

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
\caption{Frequency distribution functions of the vertical velocity (a), horizontal velocity (b), and nonlinear
vertical transport (c) are shown for a 2D run at $S = 10^{4 + 2/3}$.  We sample flows every 0.1 time units for 500 freefall
times, and include the flows at all points on the grid at each of these samples in these distributions.  All
distributions are biased by the no-slip, impenetrable boundary conditions, coupled with the dense spacing of our
Chebyshev grids near the boundaries, so there is a large peak around zero. The distributions, and thus the nonlinear
dynamics, are broadly similar, but they  (maybe?) do not pass a two-tailed Kolmogorov-Smirnov similarity test. (AUTHOR NOTE: 
I just revamped the BVP method a bit on 1/12/2018, so I haven't had the time to run full tests on all the plots here)
\label{fig:pdf_comparison} }
\end{figure}

The goodness of this method has been tested across a broad range of supercriticality.  We have
examined both Rundown and BVP solutions in the range $S = [10^{1/3}, 10^5]$ in 2D and
$S = [10^1, 10^4]$ in 3D (3D points to come).  We have also further explored up to $S = 10^6$
(AUTHOR NOTE: should we go up to $10^8$?  $10^7$ is easily in reach. Also, 3D data points are
sparse and will change -- need to rerun with proper BVP procedure).  We compare scalar, 
volume-averaged measurements of all of these runs in Fig. \ref{fig:parameter_space_comparison}.

In Fig. \ref{fig:parameter_space_comparison}a, we compare the Nusselt number scaling in 2D,
3D, and for BVP and rundown solutions.  We use a classic definition of the Nusselt number
to measure the heat transport in these systems, where
\begin{equation}
\text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
 = \frac{\angles{wT - (\text{Ra Pr})^{-1/2}\grad T}}{\angles{- (\text{Ra Pr})^{-1/2} \grad T}}.
\end{equation}
At small values of $S$, we achieve a steady state solution with a clear value of Nu.  Near
$S \sim 10^3$, our simulations begin to achieve a horizontally oscillatory state.  Due to the
use of no-slip boundaries, these states never give way to full scale shearing states, but they
do reduce the overall heat transport through the system and cause the systems to oscillate between
periods of high- and low- heat transport.  The vertical lines represent the standard deviation 
of Nu associated with these oscillations, while the error bars show the drift of the mean
value of Nu over the averaging window.  We find that $\text{Nu} \propto \text{Ra}^{1/5}$,
a weaker scaling law than that seen in traditional \RB convection \cite{johnston&doering2009},
but similar to that seen in shearing states [cite Goluskin].
(AUTHOR NOTE: Ben, I think this is entirely because of the oscillatory states.  I wonder what
would happen if we included viscous fluxes...)

In Fig. \ref{fig:parameter_space_comparison}b, we measure the rms Reynolds number, where
$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  We find that this scales roughly as
$\text{Re} \propto \text{Ra}^{0.45}$, and find good agreement between BVP and rundown solutions.

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Compensated scaling plots are shown for the Nusselt number (a), the
Reynolds number (b), and the volume-averaged temperature (c).  All plots are linear(y)-log(x),
and any differences vertically are generally small.  Symbols represent the mean value of
a measurement, vertical lines represent the standard deviation of the measurement over the
time window, and error bars represent the shift in the mean value over the window.
All data points are staggered slightly off of their original value in the x-direction
so as to show clearly the values of overlapping points at the same value of Ra. 
(a) Nu, which measures heat transport, scales roughly like $Ra^{1/5}$, and above Ra$\geq 10^6$,
simulations display horizontally oscillating plumes which have oscillating periods of high transport
and low transport.  The mean value is marginally diminished as a result, and the variance of Nu with time
is large. (b) Re, which measures the level of turbulence in the evolved solution, scales as
Ra$^{0.45}$ in 2D and (something else?) in 3D. (c) The average temperature flucutation, minus the top
temperature, which is a scalar measure of the final average thermodynamic state and should approach zero
in the limit of infinitely large Ra.
The temperature profile is slow to adjust, and differences between
BVP solutions and rundown solutions are quite easy to pick out in this measure.
\label{fig:parameter_space_comparison} }
\end{figure}

@@

>>>>

\begin{abstract}
We present a method for coupling boundary value problems (BVPs) with initial value problems (IVPs)
in order to achieve thermally converged convective solutions on dynamical timescales, rather than the
long thermal timescale. We study this method in the context of \RB convection. 
We demonstrate that the solution reached by BVP and the
solution reached by a long thermal rundown of the IVP are similar, and demonstrate that this method works at a
large range of supercriticalities.  The BVP method is used to achieve converged solutions at high supercriticality ($10^8$),
and its extensions to more complex scenarios are discussed.
\end{abstract}
\maketitle

\section{Introduction}
\label{sec:intro}
Natural convection occurs in the presence of disparate timescales. Granules on the
solar surface overturn on the order of 10 minutes, whereas deep motions in the Sun at
low Mach number are constrained by the solar rotation rate of $\sim$1 month.  
These dynamical timescales are vastly shorter than the Sun's 
Kelvin-Helmholtz timescale of nearly $3 \times 10^7$ \emph{years} \cite{stix2003}. 
Modern simulations aim to model natural convection
by increasing into the high-Rayleigh-Number (Ra) regime, in which energy transportation occurs on
timescales much larger than dynamical timescales \cite{anders&brown2017}.
In this regime, simulations must pass through a great number
of convective timescales to reach a thermally converged state.
Furthermore, as Ra increases and diffusivities correspondingly decrease, 
motions become more turbulent. To properly resolve these turbulent motions, fine grid meshes
and short timesteps are required; these requirements increase the computational
cost of evolving through a single convective overturn time.
In short, achieving thermally converged, high-Ra, astrophysically interesting
simulations is an intractably expensive problem using modern numerical tools.

@@

\section{Experiment}
\label{sec:experiment}
We adopt the Oberbeck-Boussinesq approximation.  Under this choice, the
fluid has constant kinematic viscosity ($\nu$), thermal diffusivity ($\kappa$), and coefficient
of thermal expansion ($\alpha$). The variables of the fluid that are evolved are the velocity,
$\bm{u} = u\hat{x} + v\hat{y} + w\hat{z}$, the temperature $T = T_0 + T_1$, and the pressure, $P$.
The density of the fluid is a constant, $\rho_0$, except on the
term where the constant gravitational acceleration, $\bm{g} = - g\hat{z}$, acts in the vertical momentum equation, 
where $\rho = \rho_0(1  - \alpha T_1)$.  
Under these choices, the equations of motion are \cite{spiegel&veronis1960}
\begin{gather}
\DivU = 0, 
	\label{eqn:dim_incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \bm{u}\cdot\grad\bm{u} =
-\frac{1}{\rho_0}\grad P - g( 1 - \alpha T_1)\hat{z} + \nu\grad^2\bm{u}, 
	\label{eqn:dim_bouss_momentum}
\\
\frac{\partial T_1}{\partial t} + \bm{u}\cdot\grad(T_0 + T_1) = \kappa\grad^2 T_1,
	\label{eqn:dim_bouss_energy}
\end{gather}
We non-dimensionalize these equations on the layer height ($L_z$),
the initial temperature jump across the layer ($\Delta T_0 = L_z \grad T_0$), 
and the freefall velocity ($v_{\text{ff}} = \sqrt{\alpha g L_z^2 \grad T_0}$).
by these choices, one time unit is a freefall time ($L_z/v_{ff}$).
We further re-arrange the momentum equation by introducing a reduced kinematic pressure,
$\varpi \equiv P / \rho_0 + \phi + |\bm{u}|^2 / 2$, where the gravitational
potential, $\phi$, is defined such that $\bm{g} = -\grad \phi$.
The nature of $P$ in \RB convection, as a
Lagrange multiplier,
allows the treatment of $\varpi$ as a linear variable.
We time evolve the equations in the form,
\begin{gather}
\DivU = 0, 
	\label{eqn:incompressible}
\\
\frac{\partial \bm{u}}{\partial t} + \grad \varpi - T_1\hat{z} + \mathcal{R}\grad\times\bm{\omega} = \bm{u}\times\bm{\omega}
	\label{eqn:bouss_momentum}
\\
\frac{\partial T_1}{\partial t} - \mathcal{P}\grad^2 T_1 + w \frac{\partial T_0}{\partial z} = - \bm{u}\cdot\grad T_1,
	\label{eqn:bouss_energy}
\end{gather}
where $\bm{\omega} = \grad \times \bm{u}$ is the vorticity, and the temperature
has been decomposed as $T \equiv T_0 + T_1$ where $T_0$ is the initial temperature
profile. We find Eq. (\ref{eqn:bouss_momentum}) to
be slightly faster numerically than the standard form in Eq. (\ref{eqn:dim_bouss_momentum}).
The dimensionless control parameters are set by the Rayleigh and Prandtl numbers,
\begin{equation}
\mathcal{R} \equiv \sqrt{\frac{\text{Pr}}{\text{Ra}}}, \qquad \mathcal{P} \equiv \frac{1}{\sqrt{\text{Pr}\,\text{Ra}}}, \qquad
\text{Ra} = \frac{g \alpha L_z^4 \grad T_0}{\nu\chi} = \frac{(L_z\,v_{\text{ff}})^2}{\nu\chi}, \qquad \text{Pr} = \frac{\nu}{\chi}.
\end{equation}
The dimensionless vertical extent of the domain is $z = [-1/2, 1/2]$, and at the top and bottom boundaries
we impose no-slip, impenetrable boundary conditions such that $u = v = w = 0$ at $z = \pm 1/2$.
At the lower boundary, we employ a fixed flux condition such that $\partial T_1 / \partial z = 0$
at $z = -1/2$, and we impose a fixed temperature condition of $T_1 = 0$ at $z = 1/2$. Both
horizontal directions are periodic, extending over a range $x, y = [0, \Gamma]$, where
the aspect ratio is $\Gamma = 2$. In our 2D cases, we only examine the $x$ and $z$ dimensions
and we set $v = \partial_y = 0$.

The chosen thermal boundary conditions at the upper and lower plates
determine key quantities of the evolved state.
Studies of incompressible, Boussinesq, \RB convection often
employ fixed temperature (Dirichlet) or fixed heat flux
(Neumann) boundary conditions at both plates.  
Dirichlet conditions represent plates of infinite conductivity,
whereas Neumann conditions model plates of finite conductivity.  
Both types of conditions
transport heat in the same manner \cite{johnston&doering2009},
at least when the upper and lower conditions are symmetric.
Studies of convection which aim to model
astrophysical systems such as stars often employ a mixture of these
two types of boundary conditions \cite{hurlburt&all1984, cattaneo&all1991, korre&all2017}.  
The flux at the lower boundary is fixed, modeling
the constant energy generation of the stellar core, 
while the outer boundary condition is held at a fixed temperature,
modeling the stellar surface which must output the energy generated internally.
This setup is a useful model for understanding natural
systems, but simulations which employ these boundary conditions suffer from a long 
thermal relaxation as the atmosphere loses energy and approaches the adiabat chosen by the
Dirichlet condition.  We choose these mixed conditions in part to better understand them, and in
part because these conditions minimize the number of assumptions that must be made in
setting up the boundary value problem.  For this choice of boundary conditions, the
critical Ra is Ra$_{\text{crit}} = 1295.78$, and we will often speak in terms of the
supercriticality, $S = \text{Ra}/\text{Ra}_{\text{crit}}$.

@@

\subsection{Numerics}
We utilize the 
Dedalus\footnote{\url{http://dedalus-project.org/}} 
pseudospectral framework \cite{burns&all2016} to time-evolve  
(\ref{eqn:incompressible})-(\ref{eqn:bouss_energy}) 
using an implicit-explicit (IMEX), third-order, four-step 
Runge-Kutta timestepping scheme RK443 \cite{ascher&all1997}.  
The linear terms (on the LHS of the equations) are solved implicitly,
while the nonlinear terms (RHS) are explicitly solved.
The temperature field is decomposed as $T = T_0(z) + T_1(x, y, z, t)$
and the velocity is $\bm{u} = w\bm{\hat{z}} + u\bm{\hat{x}} + v\bm{\hat{y}}$.
In our 2D runs, $v = 0$.
Variables are time-evolved on a dealiased Chebyshev (vertical)
and Fourier (horizontal, periodic) domain in which the
physical grid dimensions are 3/2 the size of the coefficient grid.

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
\caption{Comparisons of the evolved thermodynamic states of a BVP solution and a long IVP rundown at
$S = 10^{4 + 2/3}$ are shown.  (a) Evolved temperature profiles, as a function of height.
(b) The percentage difference between the temperature profiles (as shown in (a)), as a function of height.
(c) Probability distributions of point-by-point measurements of $T$ throughout the two domains over the
averaging windows are shown.  The cumulative distribution functions are overplotted and the maximum
difference between them in 0.0407. This difference arises due to the imperfect alignment of the
mean domain temperatures, but it is clear that otherwise the statistics are quite similar.
\label{fig:temp_comparison} }
\end{figure}

The temperature profiles of a 2D run at $S = 10^{4 + 2/3}$ 
for both the BVP solve and the long rundown are shown in
Fig. \ref{fig:temp_comparison}a.  While they are not perfectly aligned they are within less than
0.25\% of each other throughout the depth of the atmosphere, as shown in Fig. \ref{fig:temp_comparison}b.
While the mean temperature profile is interesting, the point-by-point fluctuations in the
temperature are what lead to convective transport, and thus examining the spread of temperature
and the allowed values that it can take are important to characterizing the system.  As seen
in Fig. \ref{fig:temp_comparison}c, aside from the noticeable difference in the mode of the
temperatures, the two runs exhibit largely the same spread of temperatures.
(AUTHOR NOTE: we aren't quite sure how to do a KS test properly here, but we can at least
list the KS statistic -- currently this is in the caption.)

In addition to examining the thermodynamics of the solutions, we are especially interested in
determining if the post-BVP solution appropriately captures key features of the nonlinear dynamics.
We show point-by-point probability distributions of the horizontal velocity, vertical velocity,
and nonlinear transport in Fig. \ref{fig:pdf_comparison}.  All of these measures have a sharp
peak at zero due to the no-slip, impenetrable boundary conditions and the denser grid sampling
near the boundaries of our Chebyshev grid.  Regardless, we see that the velocities of the 
two solutions are largely consistent.  The nonlinear transport in Fig. \ref{fig:pdf_comparison}c
shows that the rundown solution experiences a larger number of energetic, extreme events,
but the BVP displays a larger number of moderately energetic events than the IVP (as
evidenced by the differences in the cumulative distribution functions).

\begin{figure}[b]
\includegraphics[width=\textwidth]{./figs/pdf_comparison.png}
\caption{Probability distribution functions of the vertical velocity (a), horizontal velocity (b), and nonlinear
vertical transport (c) are shown for a 2D run at $S = 10^{4 + 2/3}$.  We sample flows every 0.1 time units for 500 freefall
times, and include the flows at all points on the grid at each of these samples in these distributions.  All
distributions are biased by the no-slip, impenetrable boundary conditions, coupled with the dense spacing of our
Chebyshev grids near the boundaries, so there is a large peak around zero. 
The cumulative distribution function is overplotted on each plot, with a maximum difference of
(a) 0.027, (b) 0.0061, and (c) 0.035. There is an excess of higher-flux carrying
elements in the BVP solution than in the IVP rundown, despite the rundown's distribution
having more powerful, rare events.
\label{fig:pdf_comparison} }
\end{figure}

The goodness of this method has been tested across a broad range of supercriticality.  We have
examined both Rundown and BVP solutions in the range $S = [10^{1/3}, 10^5]$ in 2D and
$S = [10^1, 10^4]$ in 3D.  We have also further explored up to $S = 10^6$
(AUTHOR NOTE: we're going up to $10^8$ in 2D right now, need to mention this is state of
the art and give refs).
We show the volume averaged Nusselt number, RMS Reynolds number, and mean temperature in
the evolved BVP solutions in in Fig. \ref{fig:parameter_space_comparison}a-c.
The relative error of the BVP measurements of these values is compared to the IVP
measurements for these values in Fig. \ref{fig:parameter_space_comparison}d-f.

In Fig. \ref{fig:parameter_space_comparison}a, we show the Nusselt number scaling in 2D and
3D.  We use a classic definition of the Nusselt number
to measure the heat transport in these systems, where
\begin{equation}
\text{Nu} = \frac{\angles{F_{\text{conv}} + F_{\text{cond}}}}{\angles{F_{\text{cond, ref}}}}
 = \frac{\angles{wT - (\text{Ra Pr})^{-1/2}\grad T}}{\angles{- (\text{Ra Pr})^{-1/2} \grad T}}.
\end{equation}
At small values of $S$, we achieve a steady state solution with a clear value of Nu.  Near
$S \sim 10^3$, our simulations begin to achieve a horizontally oscillatory state.  Due to the
use of no-slip boundaries, these states never give way to full scale shearing states, but they
do reduce the overall heat transport through the system and cause the systems to oscillate between
periods of high- and low- heat transport.  The vertical lines represent the standard deviation 
of Nu associated with these oscillations, while the error bars show the drift of the mean
value of Nu over the averaging window.  We find that $\text{Nu} \propto \text{Ra}^{1/5}$,
a weaker scaling law than that seen in traditional \RB convection \cite{johnston&doering2009},
but similar to that seen in shearing states [cite Goluskin].
(AUTHOR NOTE: Ben, I think this is entirely because of the oscillatory states.  I wonder what
would happen if we included viscous fluxes...)

In Fig. \ref{fig:parameter_space_comparison}b, we measure the rms Reynolds number, where
$\text{Re} = \angles{|\bm{u}|} / \mathcal{R}$.  We find that this scales roughly as
$\text{Re} \propto \text{Ra}^{0.45}$.

@@

For each of these measurements, the BVP achieves the same value as the IVP to
within about 3\% (Fig. \ref{fig:parameter_space_comparison}d-f).  This is good agreement,
and the residuals have a scattered distribution of positive and negative values, indicating
that the method is not biased towards the wrong answer in a clear manner.

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Scaling plots are shown for the Nusselt number (a), the
Reynolds number (b), and the volume-averaged temperature (c).  
Symbols represent the mean value of
a measurement, vertical lines represent the standard deviation of the measurement over the
time window, and error bars represent the shift in the mean value over the window.
(a) Nu, which measures heat transport, scales roughly like $Ra^{1/5}$, and above Ra$\geq 10^6$,
simulations display horizontally oscillating plumes which have oscillating periods of high transport
and low transport.  The mean value is marginally diminished as a result, and the variance of Nu with time
is large. (b) Re, which measures the level of turbulence in the evolved solution, scales as
Ra$^{0.45}$ in 2D and is not distinctly different in 3D. (c) The average temperature flucutation, minus the top
temperature, which is a scalar measure of the final average thermodynamic state and should approach zero
in the limit of infinitely large Ra.
The temperature profile is slow to adjust, and differences between
BVP solutions and rundown solutions are quite easy to pick out in this measure. (d-f)
Relative error is shown between the BVP and IVP measurements of Nu (d), Re (e), and the
mean temperature (f). The grey box indicates the region in which only BVP runs were
carried out due to computational expense.
\label{fig:parameter_space_comparison} }
\end{figure}

@@

It is important to note that the measurements made in
this paper were generally done for short timescales (a few hundred buoyancy times) in
order to show the precise differences between the BVP solutions and the IVP solutions.
Where there are differences, the BVP solution is trending towards the IVP solution,
and if measurements were taken over long timescales (e.g., a thermal time), the
differences between the BVP solution and IVP solution would be negligible.
